SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-11-02 response.tex

% \newpage
% ```
\section{Responses to the Comments from Reviewer 1}

% comment6
\rcomment{
\color{red} The text in some experimental result figures is too small to be legible. Improving the clarity and resolution is recommended.
}

Thank you for your valuable feedback regarding the legibility of the experimental result figures. We have reviewed each figure in the manuscript and enhanced the resolution and clarity to ensure that all text and details are easily readable. Specifically, we have increased the font size within the figures and adjusted the image quality to provide a sharper, more distinct presentation of the experimental results.

% 修改后的结果如图\ref{fig:lab2}所示，同时我们也修改了文章中相应的分析部分，使其更易符合实验结果并且更易理解。
\begin{figure*}[!h]
    \centering
    \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE. The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign, or vice versa. }
    \label{fig:lab2}
\end{figure*}

Figure \ref{fig:lab2} shows the image after modification. We also updated the corresponding analysis section in the article to better align with the experimental findings and enhance readability. The revised analysis is shown below:

\textcolor{blue}{SecFFT outperforms other mechanisms in handling various attack. SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes. Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 8\%, 3.9\%, and 9.5\%, respectively, with misidentified nodes more broadly distributed. Among them, FoolsGold exhibits the highest misidentification rate. It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.}

@@

\textbf{Response:} Thank you for pointing this out. Our Figure 3 corresponds to Section B, 2) of the Methodology section. We placed the image alongside the related text but did not provide a description of the content, nor was the image referenced in the article. We have now cited this image in the text and provided a brief description:

Figure 3 illustrates the first two steps of the Long-term Attack Intention Detection. The figure comprises three rows overall. The first row demonstrates the process of federated learning, where many robot nodes independently train their local models \( \theta^t_{l_1} \) based on the distributed global model \( G_{t-1} \). Each participating client then uploads its gradient updates to the central server's global model, which are aggregated to form the next global model iteration. The second row is divided into two sections: the left section shows the flattened gradients updated across multiple rounds for clients. The first column represents the gradient update of a specific round, the second column shows the flattened gradient updates from \( n \) clients in one round, and the third column displays the flattened updates across \( T \) rounds for \( n \) clients. The right section of the image represents the global model in each round. The third row depicts how a single client's intention point is calculated based on multi-round historical data, where each ray signifies the flattened results of the model updates, and the hypersphere's center represents the current client's intention point.

% comment8
\rcomment{
\color{red} The steps in the final paragraph of Section 5 do not align with Algorithm 2. Please revise for consistency.
}

% 感谢您指出文本中描述行数与算法不一致的问题。我们已根据算法的最新修改，仔细检查并修正了第五节最后一段中的行数描述，确保其与算法2的步骤完全对齐。具体来说，我们逐条对照了算法中的每个步骤，确保每个操作、条件和循环都在文本中得到了准确反映。

% 此外，我们在修订过程中还增强了描述的清晰度，以便读者能够更容易理解算法的执行流程。我们还添加了必要的背景信息和解释，以帮助读者在上下文中更好地理解每一步的意义和目的。

% 这些修改不仅提高了文本的准确性，也增强了整篇论文的逻辑连贯性。我们非常感谢您对此问题的关注，这使我们能够提升稿件的整体质量和可读性。

Thank you for pointing out the inconsistency between the line numbers described in the text and those in Algorithm 2. We have carefully reviewed and revised the final paragraph of Section 5 to ensure that it aligns perfectly with the updated steps in the algorithm. Specifically, we compared each step in the algorithm with the corresponding actions, conditions, and loops described in the text to ensure accurate representation.

In addition to correcting the line numbers, we enhanced the clarity of the descriptions during the revision process. This makes it easier for readers to understand the execution flow of the algorithm. We also added necessary background information and explanations to help readers grasp the significance and purpose of each step within the context.

These modifications not only improve the accuracy of the text but also enhance the logical coherence of the entire paper. We greatly appreciate your attention to this issue, which has allowed us to elevate the overall quality and readability of the manuscript.

\textcolor{blue}{We summarize the algorithm in the form of pseudocode, as shown in Algorithm \ref{alg:malicious-node-detection-history}. Lines 4 to 6 correspond to Step 1, which outlines the method for retaining historical records for \(T\) rounds. Lines 7 to 12 correspond to Step 2, which describes the use of the minimum enclosing hypersphere algorithm to determine each robot node's intent point and confidence level. Lines 13 to 22 correspond to Step 3, which explains how to identify normal and abnormal nodes using the LOF algorithm. Finally, lines 23 to 25 correspond to Step 4, which illustrates the method for performing weighted aggregation based on each robot node's confidence level.
}

@@

% comment9
\rcomment{
\color{red} Some conditions in Algorithm 2 are unclear, such as "for Client i do", "while Not Converged do", and "for Each point Oj $\neq$ Oi do". Clarification and revision are needed.
}

\textbf{Response:} Thank you for your valuable feedback on Algorithm 2. We have reviewed the conditions and updated the descriptions to ensure they are clear and unambiguous. Specifically:

@@

\begin{itemize}
    \item \textbf{"for Client $i$ do"}: We clarified this condition to indicate that the algorithm iterates over each client in the dataset, specifying how Client $i$ is selected and what actions are taken for each client.

    \item \textbf{"while Not Converged do"}: We revised this condition to include the specific convergence criteria used in the algorithm. This provides a clear stopping condition of $\|O_{i,k}-O_{i,k+1}\|\geq \lambda$ and $k\leq k_{max}$, ensuring that readers understand when the loop will terminate.

@@

    \item \textbf{"for Each point $O_j \neq O_i$ do"}: We clarified that this loop iterates over all points in the dataset except for point $O_i$, and we specified the purpose of comparing each $O_j$ with $O_i$ in the context of the algorithm’s objective.
\end{itemize}

% 除此之外，我们还发现了一个小细节，即原本的注释中注释符号和注释内容左右空格数量不一致，我们顺便修复了这个错误。

In addition, we also discovered a small detail that the number of spaces left and right in the original comments was inconsistent between the comment symbols and the comment content. We also fixed this error.

@@

These modifications provide a more detailed and precise description of the algorithm’s flow. We appreciate your insights and believe these clarifications enhance the readability and understanding of Algorithm 2.

% 现在的算法2伪代码如下所示：

% TODO: 现在有一个问题就是，文章中的算法2在Response中出现更早，因此编号变成了Algorithm 1
The pseudocode for Algorithm 2 is as follows:

\begin{algorithm}
\caption{Attack intention detection and secure aggregation}
\label{alg:malicious-node-detection-history}
\begin{algorithmic}[1]
\State \textbf{Input:} Global model history $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$
\State \textbf{Output:} Sets of normal clients $U_{nor}$ and malicious clients $U_{mal}$

\For {Client \textcolor{blue}{$i\in \{1\ldots N\}$}}

\State{\color{CadetBlue}/* \textbf{Construction of updates and model databases */}} 
    \State Record flattened gradients $\bar{\theta_i^t}$ and models $\theta_g^{t-1}$
    % \State $\widetilde{\theta_{i}^{t'-1}}  \gets Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'}  \gets \overline{\triangledown\theta_{i}^{t'}}$ for $t'  \gets \max\{t-T+1, 1\}, \ldots, t$ \Comment{Construct rays}
    \State Construct rays for each $'$, $\max\{t-T+1, 1\}\leq t' \leq t$

\State{\color{CadetBlue}/* \textbf{Construction of attack intention */}}

    \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
    \While {\textcolor{blue}{$\|O_{i,k}-O_{i,k+1}\|\geq \lambda$ and $k\leq k_{max}$}}
        \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
    \EndWhile
    \State  $cre_i  \gets \frac{1}{r_i + \rho}$ \Comment{Calculate confidence}

\State{\color{CadetBlue}/* \textbf{LOF-driven malicious intention detection */}}

    \For {Each point $O_j \neq O_i$\textcolor{blue}{, $j\in\{1\ldots N\}$}}
        \State Calculate distance $\|O_i - O_j\|$
    \EndFor
    \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
    \State $rea_{i,j}  \gets \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$  \Comment{Compute reachability distance}
    \State  $lrd_i  \gets \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$ \Comment{Calculate reachability density}
    \State $lof_i  \gets \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$

% \For {Client $i$}
%     \State Compute $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
%     \If {$lof_i > 1$}
%         \State Mark client $i$ as malicious, add to $U_{mal}$
%     \Else
%         \State Mark client $i$ as normal, add to $U_{nor}$
%     \EndIf
% \EndFor
% \State $U_{mal} = \{i \,|\, lof_i > 1\}$
% \State $U_{nor} = \{i \,|\, lof_i \leq 1\}$
\State $U_{mal}, U_{nor}  \gets \{i \,|\, lof_i > 1\}, \{i \,|\, lof_i \leq 1\}$

\State{\color{CadetBlue}/* \textbf{Secure aggregation of global FFT model */}} 
        \State $cre_i'  \gets \tanh(cre_i)$\Comment{Compute adjusted confidence}
        \State $w_i  \gets \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$\Comment{Normalize weights}
\EndFor

\State \textbf{Output:} $\theta_g^t \gets \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$\Comment{Aggregate global model}
\end{algorithmic}
\end{algorithm}

% comment10
\rcomment{
\color{red} Section VI-C lacks quantitative analysis of the experimental results. The partitioning results in Fig. 6 are hard to distinguish, and the font size is too small. Moreover, the four subplots lack necessary labels, and the same issues are present in Fig. 7.
}
\textbf{Response:} 
Thank you for your valuable comments and suggestions, which have greatly helped us to improve our paper. We have carefully addressed each of the issues you raised and made the following modifications:

First, we recognized the need for a more in-depth quantitative analysis in this section. We have now included additional statistical data to provide a comprehensive analysis of the experimental results, including metrics that better quantify the effectiveness of our partitioning method. This has been added to enhance the clarity and significance of our findings.
The following are the corresponding modifications in the article:

\textcolor{blue}{This indicates that SecFFT effectively defends against attacks by accurately identifying and neutralizing malicious users, all while preserving the performance and accuracy of the global model. In contrast, other defense mechanisms perform less effectively. Although Flame also shows strong performance in reducing ASR and mitigating malicious attack, it introduces considerable noise in the identification process, leading to a decrease in TSR, especially under MR attacks, where the performance degradation is more pronounced. FLTrust fails to defend effectively, with ASR initially low in MR attacks but quickly rising after several iterations, ultimately proving ineffective; against NEUR and EDGE CASE attacks, ASR remains high from the outset, demonstrating inadequate defense. Foolsgold also shows poor performance in defending against all three types of attacks, maintaining a high ASR from the beginning. Overall, the comparison highlights that other defense mechanisms either fail to effectively resist attacks or compromise model performance during defense. This further underscores SecFFT's significant advantage in federated fine-tuning for backdoor attack resistance, making it the optimal defense choice.}

\textcolor{blue}{SecFFT outperforms other mechanisms in handling various attack. SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes. Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 8\%, 3.9\%, and 9.5\%, respectively, with misidentified nodes more broadly distributed. Among them, FoolsGold exhibits the highest misidentification rate. It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.}

Second, to improve the visibility and distinguish-ability of the partitioning results in Figure 6, we have added a supplementary sub-image that provides a clearer presentation of the partitioned sections. We also increased the font size to enhance readability, ensuring that key features are visible and easy to interpret. For details, please refer to Figure \ref{fig:lab1} and responses to the comment 2 from Reviewer 2.

Third, we re-adjusted the layout of Figure 7 to address the issues you pointed out. Specifically, we improved the font sizes, added necessary labels, and modified the legend for better comprehension. These adjustments were made to ensure that the experimental data in Figure 7 are both readable and visually clear. For details, please refer to Figure \ref{fig:lab2} and responses to the comment 1 from Reviewer 1.

% comment11
\rcomment{
\color{red} Some of the English expressions are difficult to understand. Improving the overall quality of writing is recommended.
}
\textbf{Response:} 
Thank you for your feedback and suggestions for improving the clarity of our paper. We acknowledge that some English expressions may have been difficult to understand, and we appreciate your recommendation to enhance the overall quality of writing.To address this concern, we have revised the manuscript, focusing on improving the fluency and readability of the text. We have rephrased complex or unclear expressions to ensure that the language is more straightforward and easier to follow. Additionally, we have performed a detailed grammar and style check to improve the overall quality of writing.

@@

% comment20
\rcomment{
\color{red} The manuscript’s language requires improvement, as there are multiple grammatical errors and unclear expressions. A thorough revision is suggested to enhance overall readability.
}
\textbf{Response:} 
Thank you for your valuable feedback. We appreciate your comments regarding the grammatical errors and unclear expressions in the manuscript.

In response, we have undertaken a comprehensive revision of the paper, with particular attention to correcting grammatical mistakes and improving the clarity of the text. We have also simplified complex expressions and enhanced the overall readability to ensure the content is more accessible and coherent.

\newpage

%=================================
\section{Responses to the Comments from Reviewer 3}
%=================================
%=================================
%========================================================
\rcomment{
\color{red} The technical framework lacks sufficient explanatory detail. For example, the steps in Fig. 2 are explained too briefly, making them difficult to understand.
}

\textbf{Response:} 
Thank you for your valuable feedback. We appreciate your insights, especially regarding the need for further detail in the technical framework explanation and the steps illustrated in Figure 2.

In response, we have carefully considered your suggestions and revised the framework diagram to enhance clarity and detail. The new version of Figure 2 (which depicted as Figure \ref{fig2:instant}) has been redrawn to illustrate each step in the algorithm more thoroughly, ensuring that readers can understand the entire process without ambiguity. We have added comprehensive explanations for each step, including intermediate processes and transitions, to provide a clearer and more accessible description of the framework. These changes are intended to ensure that the entire flow of the framework is presented in a more intuitive and informative manner.

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\linewidth]{figures/secfft-1.pdf}
    \caption{SecFFT's instantaneous attack behavior perception module with frequency-domain deep outlier feature semantics extraction}
    \label{fig2:instant}
\end{figure}

@@

%========================================================
\rcomment{
\color{red} In Algorithm 1, there are unused variables in line 5.
}
% 问题：算法1第5行出现未使用变量。

\textbf{Response:} We thank the Reviewer for the constructive comment, and
% 非常抱歉，因为我们的疏忽，导致该算法出现让人无法理解的地方。根据您的建议，我们修改了该算法的相关部分，删除了未使用的变量。同时为了使整个算法过程更易理解，我们修改了另外一些跟原文不一致的地方，\ref{alg:malicious-node-detection}展示了修改后的结果。
we sincerely apologize for the confusion caused by the oversight in our algorithm.
Following your suggestion, we revised the relevant parts of the algorithm and removed unused variables.
Additionally, to make the entire algorithm process easier to understand, we adjusted some parts that were inconsistent with the original text, and algorithm \ref{alg:malicious-node-detection} shows the modified result.
% 最后，为了表现算法中某些变量会随训练轮次所变化，我们给一些变量添加时间$t$的上标，比如修改$C_{max},Chi_i^2,{C_1}', {C_2}'$至$C^t_{max},{Chi^t_i}^2,{C^t_1}', {C^t_2}'$
Finally, to represent that certain variables in the algorithm change with the training rounds, we added the superscript of round $t$ to some variables, such as modifying $C_{max}, Chi_i^2, {C'_1}, {C'_2}$ to $C^t_{max}, {Chi^t_i}^2, {C^t_1}', {C^t_2}'$.

% 图1展示了算法修改后的结果
The Algorithm \ref{alg:malicious-node-detection} shows the result of the modified algorithm.

### 2024-11-02 main-v2.tex
yesterday: archive - mainly me
先协助学弟把OWA迁移过去

\subsection{Instantaneous Attack Behavior Perception}
\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{figures/fig2.png}
    \caption{SecFFT's instantaneous attack behavior perception module with frequency-domain deep outlier feature semantics extraction}
    \label{fig2:instant}
\end{figure}
%^\textbf{Motivation:} 目前的防御策略主要集中于利用攻击的“浅层语义特征”来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向\cite{foolsgold}，范数\ref{sun2019can}以及几何中心\cite{pillutla2022robust}等几何或者统计特性。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意更新，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意更新。同时最新的研究表明\cite{huang2023multi}，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性更新，因为这些方法往往受到维度灾难的影响。此外攻击策略也在不停的演变，现在的攻击者已经能够通过精心调整，使恶意更新在方向、范数等浅层特征上与良性更新相似，从而巧妙地避开这些基于浅层语义特征的防御措施，最终在全局模型中植入后门。但尽管攻击者的攻击策略变得越来越复杂，值得注意的是，后门攻击的本质在于让模型建立起预定义触发器和目标之间的联系，因此无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新相较于良性用户始终在某种分布上具有偏移。
\textbf{Motivation:} 
Current defense strategies primarily focus on identifying malicious nodes by leveraging shallow semantic features of the attack, such as the direction \cite{foolsgold}, magnitude \cite{sun2019can}, and geometric or statistical properties like geometric centers \cite{pillutla2022robust} of updates. However, these defense methods based on shallow semantic features face significant limitations in high-dimensional spaces. First, these methods are only effective against certain types of attacks under specific assumptions. For example, cosine distance can detect malicious updates with large directional deviations, while Euclidean distance is used to detect malicious updates that affect the global model by increasing the $L_2$ norm. Furthermore, recent studies \cite{huang2023multi} have shown that traditional distance metrics, such as Euclidean distance, cannot effectively distinguish between malicious and benign updates in high-dimensional spaces due to the curse of dimensionality. Additionally, attack strategies are constantly evolving, and attackers can now carefully adjust their malicious updates to resemble benign updates in terms of direction, magnitude, and other shallow features. This allows them to bypass defenses based on shallow semantic features and eventually implant backdoors into the global model. \textcolor{red}{Despite the increasingly sophisticated strategies employed by attackers, it is important to note that the essence of backdoor attacks lies in establishing a link between the predefined trigger and the target within the model. Thus, regardless of how attackers adjust their attack strategies, their updates will always exhibit some distributional shift compared to benign nodes.}

@@

We summarize the algorithm in the form of pseudocode, as shown in Algorithm \ref{alg:malicious-node-detection-history}. Lines 3 to 7 correspond to Step 1, which outlines the method for retaining historical records for \(T\) rounds. Lines 8 to 15 correspond to Step 2, which describes the use of the minimum enclosing hypersphere algorithm to determine each robot node's intent point and confidence level. Lines 16 to 27 correspond to Step 3, which explains how to identify normal and abnormal nodes using the LOF algorithm. Finally, lines 28 to 32 correspond to Step 4, which illustrates the method for performing weighted aggregation based on each robot node's confidence level.

@@

% \For {Client $i$ \in 55}
\State{\color{CadetBlue}/* \textbf{Construction of updates and model databases */}} 
    \State Record flattened gradients $\bar{\theta_i^t}$ and models $\theta_g^{t-1}$
    % \State $\widetilde{\theta_{i}^{t'-1}}  \gets Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'}  \gets \overline{\triangledown\theta_{i}^{t'}}$ for $t'  \gets \max\{t-T+1, 1\}, \ldots, t$ \Comment{Construct rays}
    \State Construct rays for each $'$, $\max\{t-T+1, 1\}\leq t' \leq t$

@@

    \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
    \While {Not Converged}
        \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
    \EndWhile
    \State  $cre_i  \gets \frac{1}{r_i + \rho}$ \Comment{Calculate confidence}

\State{\color{CadetBlue}/* \textbf{LOF-driven malicious intention detection*/}}

    \For {Each point $O_j \neq O_i$}
        \State Calculate distance $\|O_i - O_j\|$
    \EndFor
    \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
    \State $rea_{i,j}  \gets \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$  \Comment{Compute reachability distance}
    \State  $lrd_i  \gets \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$ \Comment{Calculate reachability density}
    \State $lof_i  \gets \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$

@@

\State{\color{CadetBlue}/* \textbf{Secure aggregation of global FFT model*/}} 
        \State $cre_i'  \gets \tanh(cre_i)$\Comment{Compute adjusted confidence}
        \State $w_i  \gets \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$\Comment{Normalize weights}
\EndFor

@@

\textbf{Evaluation metrics:}
% 就像其他文章中的评价指标一样，我们使用两个关键指标来评估投毒攻击与防御方法的效果，即ASR（攻击成功率）和 TSR（测试成功率）。ASR表示恶意节点成功诱导全局模型成功预测指定目标的概率。攻击者的目标是最大化ASR，而有效的防御措施则旨在防止ASR上升。TSR表示全局模型在测试集上的预测正确率。攻击者的目标是尽量维持模型的TSR不变，以避免被轻易检测到，而有效的防御措施则不应显著降低全局模型的TSR。
% Similar to evaluation metrics used in other works\cite{tang2023port, jin2024learning, rong2023special}, we use two key metrics to assess the effectiveness of poisoning attacks and defense methods: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate). ASR represents the probability that malicious nodes successfully induce the global model to predict the specified target. The goal of the attacker is to maximize ASR, while effective defense measures aim to prevent an increase in ASR. TSR represents the accuracy of the global model on the test set. The attacker's goal is to maintain the TSR of the model as unchanged as possible to avoid easy detection, while effective defense measures should not significantly reduce the TSR.
\textcolor{red}{For single round recognition,} similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate). ASR denotes the probability that malicious nodes successfully manipulate the global model to predict a specified target. The attacker aims to maximize the ASR, whereas effective defense mechanisms strive to prevent an increase in ASR. TSR indicates the accuracy of the global model on the test set. The attacker aims to keep the TSR of the model as stable as possible to avoid easy detection, whereas effective defense mechanisms should not significantly degrade the TSR. \textcolor{red}{For multi round recognition, ``Acc" refers to accuracy, which measures the proportion of correct predictions;``Rec" stands for recall, representing the model's ability to correctly identify positive instances;``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive;``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative;``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}

\begin{figure*}[!t]
    \centering
    \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE dimensionality reduction. The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign and benign nodes incorrectly identified as malicious. }
    \label{fig:lab2}
\end{figure*}

>>>>

\subsection{Instantaneous Attack Behavior Perception}
\begin{figure}[!t]
    \centering
    \includegraphics[width=1\linewidth]{figures/secfft-1.pdf}
    \caption{SecFFT's instantaneous attack behavior perception module with frequency-domain deep outlier feature semantics extraction}
    \label{fig2:instant}
\end{figure}
%^\textbf{Motivation:} 目前的防御策略主要集中于利用攻击的“浅层语义特征”来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向\cite{foolsgold}，范数\ref{sun2019can}以及几何中心\cite{pillutla2022robust}等几何或者统计特性。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意更新，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意更新。同时最新的研究表明\cite{huang2023multi}，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性更新，因为这些方法往往受到维度灾难的影响。此外攻击策略也在不停的演变，现在的攻击者已经能够通过精心调整，使恶意更新在方向、范数等浅层特征上与良性更新相似，从而巧妙地避开这些基于浅层语义特征的防御措施，最终在全局模型中植入后门。但尽管攻击者的攻击策略变得越来越复杂，值得注意的是，后门攻击的本质在于让模型建立起预定义触发器和目标之间的联系，因此无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新相较于良性用户始终在某种分布上具有偏移。
\textbf{Motivation:} 
Current defense strategies primarily focus on identifying malicious nodes by leveraging shallow semantic features of the attack, such as the direction \cite{foolsgold}, magnitude \cite{sun2019can}, and geometric or statistical properties like geometric centers \cite{pillutla2022robust} of updates. However, these defense methods based on shallow semantic features face significant limitations in high-dimensional spaces. First, these methods are only effective against certain types of attacks under specific assumptions. For example, cosine distance can detect malicious updates with large directional deviations, while Euclidean distance is used to detect malicious updates that affect the global model by increasing the $L_2$ norm. Furthermore, recent studies \cite{huang2023multi} have shown that traditional distance metrics, such as Euclidean distance, cannot effectively distinguish between malicious and benign updates in high-dimensional spaces due to the curse of dimensionality. Additionally, attack strategies are constantly evolving, and attackers can now carefully adjust their malicious updates to resemble benign updates in terms of direction, magnitude, and other shallow features. This allows them to bypass defenses based on shallow semantic features and eventually implant backdoors into the global model. \textcolor{red}{Despite the increasingly sophisticated strategies employed by attackers, it is important to note that the essence of backdoor attacks lies in establishing a link between the predefined trigger and the target within the model. Thus, regardless of how attackers adjust their attack strategies, their updates will always exhibit some distributional shift compared to benign nodes.}

@@

We summarize the algorithm in the form of pseudocode, as shown in Algorithm \ref{alg:malicious-node-detection-history}. Lines \textcolor{red}{4 to 6} correspond to Step 1, which outlines the method for retaining historical records for \(T\) rounds. Lines \textcolor{red}{7 to 12} correspond to Step 2, which describes the use of the minimum enclosing hypersphere algorithm to determine each robot node's intent point and confidence level. Lines \textcolor{red}{13 to 22} correspond to Step 3, which explains how to identify normal and abnormal nodes using the LOF algorithm. Finally, lines \textcolor{red}{23 to 25} correspond to Step 4, which illustrates the method for performing weighted aggregation based on each robot node's confidence level.

@@

\For {Client \textcolor{red}{$i\in \{1\ldots N\}$}}

\State{\color{CadetBlue}/* \textbf{Construction of updates and model databases */}} 
    \State Record flattened gradients $\bar{\theta_i^t}$ and models $\theta_g^{t-1}$
    % \State $\widetilde{\theta_{i}^{t'-1}}  \gets Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'}  \gets \overline{\triangledown\theta_{i}^{t'}}$ for $t'  \gets \max\{t-T+1, 1\}, \ldots, t$ \Comment{Construct rays}
    \State Construct rays for each $'$, $\max\{t-T+1, 1\}\leq t' \leq t$

@@

    \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
    \While {\textcolor{red}{$\|O_{i,k}-O_{i,k+1}\|\geq \lambda$ and $k\leq k_{max}$}}
        \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
    \EndWhile
    \State  $cre_i  \gets \frac{1}{r_i + \rho}$ \Comment{Calculate confidence}

\State{\color{CadetBlue}/* \textbf{LOF-driven malicious intention detection */}}

    \For {Each point $O_j \neq O_i$\textcolor{red}{, $j\in\{1\ldots N\}$}}
        \State Calculate distance $\|O_i - O_j\|$
    \EndFor
    \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
    \State $rea_{i,j}  \gets \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$  \Comment{Compute reachability distance}
    \State  $lrd_i  \gets \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$ \Comment{Calculate reachability density}
    \State $lof_i  \gets \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$

@@

\State{\color{CadetBlue}/* \textbf{Secure aggregation of global FFT model */}} 
        \State $cre_i'  \gets \tanh(cre_i)$\Comment{Compute adjusted confidence}
        \State $w_i  \gets \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$\Comment{Normalize weights}
\EndFor

@@

\textbf{Evaluation metrics:}
% 就像其他文章中的评价指标一样，我们使用两个关键指标来评估投毒攻击与防御方法的效果，即ASR（攻击成功率）和 TSR（测试成功率）。ASR表示恶意节点成功诱导全局模型成功预测指定目标的概率。攻击者的目标是最大化ASR，而有效的防御措施则旨在防止ASR上升。TSR表示全局模型在测试集上的预测正确率。攻击者的目标是尽量维持模型的TSR不变，以避免被轻易检测到，而有效的防御措施则不应显著降低全局模型的TSR。
% Similar to evaluation metrics used in other works\cite{tang2023port, jin2024learning, rong2023special}, we use two key metrics to assess the effectiveness of poisoning attacks and defense methods: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate). ASR represents the probability that malicious nodes successfully induce the global model to predict the specified target. The goal of the attacker is to maximize ASR, while effective defense measures aim to prevent an increase in ASR. TSR represents the accuracy of the global model on the test set. The attacker's goal is to maintain the TSR of the model as unchanged as possible to avoid easy detection, while effective defense measures should not significantly reduce the TSR.
\textcolor{red}{For instantaneous attack behavior perception,} similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate). ASR denotes the probability that malicious nodes successfully manipulate the global model to predict a specified target. The attacker aims to maximize the ASR, whereas effective defense mechanisms strive to prevent an increase in ASR. TSR indicates the accuracy of the global model on the test set. The attacker aims to keep the TSR of the model as stable as possible to avoid easy detection, whereas effective defense mechanisms should not significantly degrade the TSR. \textcolor{red}{For long-term attack intention detection, ``Acc" refers to accuracy, which measures the proportion of correct predictions;``Rec" stands for recall, representing the model's ability to correctly identify positive instances;``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive;``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative;``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}

\begin{figure*}[!t]
    \centering
    \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE. The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign, or vice versa. }
    \label{fig:lab2}
\end{figure*}
